NOSQL INSIDE SQL

### 2018-03-25 pgconfus2018/presentation.tex
Few more slides for developers side

\begin{frame}
    \frametitle{}
    \begin{center}
    \end{center}
\end{frame}

>>>>

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{Introduction}

        \begin{itemize}[label={}]
            \item Less benchmarks
            \item More opinionated best practices
        \end{itemize}

    \end{center}
\end{frame}

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{Introduction}

        \begin{itemize}[label={}]
            \item Application developers
            \item DBAs
            \item Extension developers
        \end{itemize}

    \end{center}
\end{frame}

\fontsize{13pt}{14}\selectfont
\section{Application developers}
\fontsize{17pt}{18}\selectfont

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{When jsonb?}
        \begin{itemize}
            \item <+->
        \end{itemize}

        \begin{itemize}[label={\MVRightarrow}]
            \item <+-> You have a distinct flexible model
            \item <+-> You need to work with data provided in document oriented format
            \item <+-> Workaround for technical issues (large number of tables or expensive alignment)
        \end{itemize}

    \end{center}
\end{frame}
\note{
    technical reasons - Because of some performance issues you want to keep
    number of relations as small as possible (so, you denormalize some data),
    or you're playing with alignment
}

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{When not jsonb?}
        \begin{itemize}
            \item <+->
        \end{itemize}

        \begin{itemize}[label={\MVRightarrow}]
            \item <+-> Flexibility "just in case"
            \item <+-> Reluctance to create a migration
            \item <+-> Use jsonb column as a "garbage can"
        \end{itemize}

    \end{center}
\end{frame}

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{Jsonb <-> Relation}

        \begin{columns}[T,onlytextwidth]
        \column{0.5\textwidth}
        \begin{itemize}[leftmargin=*]
            \item \includegraphics[width=6cm,height=5cm]{relation.png}
        \end{itemize}

        \vspace{20pt}

        \column{0.5\textwidth}
        \begin{itemize}[leftmargin=*]
            \item \includegraphics[width=6cm,height=5cm]{document.jpg}
        \end{itemize}
        \end{columns}

    \end{center}
\end{frame}

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{When to move from jsonb to relation?}
        \begin{itemize}
            \item <+->
        \end{itemize}

        \begin{itemize}[label={\MVRightarrow}]
            \item <+-> Queries rely significantly in information about\\
                internal structure of documents
            \item <+-> There are too many constraints for documents
            \item <+-> Some parts of document are used much more\\
                frequently than other
        \end{itemize}

    \end{center}
\end{frame}

\begin{frame}
    \frametitle{}
    \begin{center}

        \inputminted[
            fontsize=\normalsize,
        ]{sql}{sql/complex_where.sql}

    \end{center}
\end{frame}
